---
title: "simpleRegress"
author: "Milton Rodas"
date: "October 11,2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
Neck has a Adjusted R-Squared of 0.87, and a Residual Standard Error of 43.91.


```{r}
simp <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(simp)
summary.lm(simp)
```
   Age has a Adjusted R-Squared of 0.55, and a Residual Standard error of 81.47.


```{r}
simp <- lm(WEIGHT~HEADLEN,data=bears)
plot(WEIGHT~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```
   HeadLen has a Adjusted R-Squared of 0.69, and a Residual Standard Error of 67.81. 


```{r}
simp <- lm(WEIGHT~HEADWTH,data=bears)
plot(WEIGHT~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```
   HeadWth has a Adjusted R-Squared of 0.6064, and a Residual Standard Error of 76.41.


```{r}
simp <- lm(WEIGHT~LENGTH,data=bears)
plot(WEIGHT~LENGTH,data=bears)
abline(simp)
summary.lm(simp)
```
   Length has a Adjusted R-Squared of 0.7423, and a Residual Standard Error of 61.83.


```{r}
simp <- lm(WEIGHT~CHEST,data=bears)
plot(WEIGHT~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```
   Chest has a Adjusted R-Squared of 0.9262, and a Residual Standard Error of 33.08. As we see our winner in first place is CHEST!


## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

